ComBatLS Varying-Ratio Results

### 2025-01-22 paper_prop_results.Rmd

```{r}
aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")
#write out new dk atlas w/o medial wall
dk_nomed <- dk
dk_nomed$data <- dk_nomed$data %>%
  dplyr::filter(!is.na(region) & region !="corpus callosum")
#plotting info from dk atlas
dk.parc <- dk_nomed$data %>%
  as.data.frame() %>%
  na.omit() %>%
  dplyr::select(c(hemi, region, label)) %>%
  distinct()
```

@@

```{r}
cent.feat.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_cent_sex_bias_tests.RDS"))
cent.feat.sex.test.df <- bind_rows(cent.feat.sex.test.list) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))
```

@@

```{r}
cent.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

sig.sex_diff.violin <- cent.feat.sex.test.df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot() +
  geom_violin(aes(x=prop, y=median_sex_diff, fill=dataset, color=dataset)) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

@@

stats_sex.centile_for_plot <- inner_join(cent.sex_comp_tbl2, cent.feat.test_global)
#kinda hacky way of fixing positions
stats_sex.centile_for_plot.corrected <- stats_sex.centile_for_plot %>%
  mutate(p.adj.signif = ifelse(sig_fdr == "FALSE", "ns", "*"),
         y.position=case_when(dataset=="cf.gam" ~ max_cf.gam*100+0.5,
                           dataset=="cf.gamlss" ~ max_cf.gamlss*100+0.5,
                           TRUE ~ NA))

sex_err_ratio.plt <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("GMV", "sGMV", "Ventricles", "WMV"), ordered = TRUE),
         diff = diff*100,
         pheno_prop = paste(pheno, prop, sep="&")) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  labs(fill="Sex", color="Sex")+
  stat_pvalue_manual(stats_sex.centile_for_plot.corrected, label = "p.adj.signif", label.size = 2, tip.length = 0) +
  facet_grid(dataset ~ pheno, labeller=labeller(dataset=dataset_names), scales="free_x")
sex_err_ratio.plt
```

```{r}
t.test.cent.sex.diff <- cent.feat.sex.test.df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  group_by(dataset, prop) %>%
  summarise(w.test.p = tidy(wilcox.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)*100) %>% #test median of each distribution against 0, then scale to centiles
  mutate(p.val_fdr = p.adjust(w.test.p, method="fdr", n = (4*11)),
         y_pos = max_val + 0.5) %>%
  add_significance("p.val_fdr", cutpoints = c(0, 0.001, 0.01, 0.05, 1),
  symbols = c("***", "**", "*", "ns"))

@@

cent_sex_diff.plt2 <- cent.feat.sex.test.df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
  geom_jitter(size=0.4, alpha=0.1) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = p.val_fdr.signif, y = y_pos),
              data = t.test.cent.sex.diff) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
cent_sex_diff.plt2

ggsave("figs/cent_sex_diff.plt2.jpeg", cent_sex_diff.plt2)
```

@@

Test sex-differences in centile errors w/in each feature
```{r}
noext_cent.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext_cent.feat.sex.test.df <- bind_rows(noext_cent.subj.sex.test.list)
```

@@

```{r}
noext_cent.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

noext_cent.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

noext_t.test.cent.sex.diff <- noext_cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_fdr = case_when(
           # p.val_fdr < 0.001 ~ "***",
           #                     p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
           #                     p.val_fdr >= 0.01 & 
                               p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = ifelse(max_val < 0, ((max_val*100)*0.5), (max_val*100)+0.8))

noext_cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_fdr, y = y_pos),
              data = noext_t.test.cent.sex.diff[which(noext_t.test.cent.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

@@

```{r}
z.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_sex_bias_tests.RDS"))
z.feat.sex.test.df <- bind_rows(z.sex.test.list)
```

@@

```{r}
z.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

z.sig.sex_diff.violin <- z.feat.sex.test.df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  ggplot() +
  geom_violin(aes(x=prop, y=median_sex_diff, fill=dataset, color=dataset)) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z-Score Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

@@

@@

t.test.z.sex.diff <- z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_fdr = case_when(p.val_fdr < 0.05 ~ "*",
                            p.val_fdr >= 0.05 ~ ""),
         y_pos = max_val+0.005)

z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_fdr, y = y_pos),
              data = t.test.z.sex.diff[which(t.test.z.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
```

```{r}
z.t.test.cent.sex.diff <- z.feat.sex.test.df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  group_by(dataset, prop) %>%
  summarise(w.test.p = tidy(wilcox.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(w.test.p, method="fdr", n = (4*11)), 
         y_pos = max_val + 3) %>%
  add_significance("p.val_fdr", cutpoints = c(0, 0.001, 0.01, 0.05, 1),
  symbols = c("***", "**", "*", "ns"))

z.cent_sex_diff.plt <- z.feat.sex.test.df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
  geom_jitter(size=0.4, alpha=0.1) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = p.val_fdr.signif, y = y_pos),
              data = z.t.test.cent.sex.diff) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z-Score Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
z.cent_sex_diff.plt

@@

```{r}
noext_z.feat.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext_z.feat.sex.test.df <- bind_rows(noext_z.feat.sex.test.list)
```

@@

```{r}
noext_z.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

noext_z.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

>>>>

```{r}
remotes::install_github("BGDlab/ggsegTissue")
library(ggsegTissue)
#write out new dk atlas w/o medial wall
dk_nomed <- dk
dk_nomed$data <- dk_nomed$data %>%
  dplyr::filter(!is.na(region) & region !="corpus callosum")
#plotting info from dk atlas
dk.parc <- dk_nomed$data %>%
  as.data.frame() %>%
  na.omit() %>%
  dplyr::select(c(hemi, region, label)) %>%
  distinct()
```

@@

```{r}
cent.feat.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_cent_sex_bias_tests.RDS"))

cent.feat.sex.test.df <- bind_rows(cent.feat.sex.test.list) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      sig_uncor = ifelse(p.value<0.05, TRUE, FALSE)) %>%
  mutate(significant = case_when(sig_fdr == TRUE ~ "Survives FDR Correction",
                                 sig_uncor == TRUE & sig_fdr == FALSE ~ "Uncorrected Only",
                                 sig_uncor == FALSE & sig_fdr == FALSE ~ "Not Significant")) %>%
  mutate(significant = factor(significant, ordered=TRUE, levels=c("Survives FDR Correction", "Uncorrected Only", "Not Significant")))
```

@@

```{r}
cent.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=significant)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

sig.sex_diff.violin <- cent.feat.sex.test.df %>%
  dplyr::filter(sig_uncor == TRUE) %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot() +
  geom_violin(aes(x=prop, y=median_sex_diff, fill=dataset, color=dataset)) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

@@

stats_sex.centile_for_plot <- inner_join(cent.sex_comp_tbl2, cent.feat.test_global)
table(stats_sex.centile_for_plot$significant)

#kinda hacky way of fixing positions
stats_sex.centile_for_plot.corrected <- stats_sex.centile_for_plot %>%
  mutate(p.signif = ifelse(sig_uncor == "FALSE", "ns", "*"),
         y.position=case_when(dataset=="cf.gam" ~ max_cf.gam*100+0.5,
                           dataset=="cf.gamlss" ~ max_cf.gamlss*100+0.5,
                           TRUE ~ NA))

sex_err_ratio.plt <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("GMV", "sGMV", "Ventricles", "WMV"), ordered = TRUE),
         diff = diff*100,
         pheno_prop = paste(pheno, prop, sep="&")) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  labs(fill="Sex", color="Sex")+
  stat_pvalue_manual(stats_sex.centile_for_plot.corrected, label = "p.signif", label.size = 2, tip.length = 0) +
  facet_grid(dataset ~ pheno, labeller=labeller(dataset=dataset_names), scales="free_x")
sex_err_ratio.plt
```

```{r}
t.test.cent.sex.diff <- cent.feat.sex.test.df %>%
  #dplyr::filter(sig_fdr == TRUE) %>%
  group_by(dataset, prop) %>%
  summarise(w.test.p = tidy(wilcox.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)*100) %>% #test median of each distribution against 0, then scale to centiles
  mutate(p.val_fdr = p.adjust(w.test.p, method="fdr", n = (11)),
         y_pos = max_val + 0.25) %>%
  add_significance("p.val_fdr", cutpoints = c(0, 0.001, 0.01, 0.05, 1),
  symbols = c("***", "**", "*", "ns")) %>%
  add_significance("w.test.p", cutpoints = c(0, 0.001, 0.01, 0.05, 1),
  symbols = c("***", "**", "*", "ns"))

@@

#w/ fdr correction
cent.feat.sex.test.df %>%
  #dplyr::filter(sig_uncor == TRUE) %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
  geom_jitter(size=0.4, alpha=0.1) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = p.val_fdr.signif, y = y_pos),
              data = t.test.cent.sex.diff) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

cent_sex_diff.plt2 <- cent.feat.sex.test.df %>%
  #dplyr::filter(sig_uncor == TRUE) %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
  geom_jitter(size=0.4, alpha=0.1) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), scales="free_y") + 
  geom_text(aes(label = w.test.p.signif, y = y_pos),
              data = t.test.cent.sex.diff) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
cent_sex_diff.plt2

ggsave("figs/cent_sex_diff.plt2.jpeg", cent_sex_diff.plt2)
sfig13 <- ggarrange(sex_err_ratio.plt, cent_sex_diff.plt2,
          nrow=2,
          heights = c(.7, 1),
          labels = "AUTO")
ggsave("figs/sfig13.jpeg", sfig13, height=9, width=7)
```

@@

Test sex-differences in centile errors w/in each feature
```{r}
noext_cent.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext_cent.feat.sex.test.df <- bind_rows(noext_cent.subj.sex.test.list) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      sig_uncor = ifelse(p.value<0.05, TRUE, FALSE)) %>%
  mutate(significant = case_when(sig_fdr == TRUE ~ "Survives FDR Correction",
                                 sig_uncor == TRUE & sig_fdr == FALSE ~ "Uncorrected Only",
                                 sig_uncor == FALSE & sig_fdr == FALSE ~ "Not Significant")) %>%
  mutate(significant = factor(significant, ordered=TRUE, levels=c("Survives FDR Correction", "Uncorrected Only", "Not Significant")))
```

@@

```{r}
noext_cent.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=significant)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

noext_cent.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_uncor == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

noext_t.test.cent.sex.diff <- noext_cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_uncor = case_when(t.test.p < 0.05 ~ "*",
                               t.test.p >= 0.05 ~ ""),
         y_pos = ifelse(max_val < 0, ((max_val*100)*0.5), (max_val*100)+0.8))

noext_cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_uncor, y = y_pos),
              data = noext_t.test.cent.sex.diff[which(noext_t.test.cent.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

@@

```{r}
z.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_sex_bias_tests.RDS"))
z.feat.sex.test.df <- bind_rows(z.sex.test.list) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      sig_uncor = ifelse(p.value<0.05, TRUE, FALSE)) %>%
  mutate(significant = case_when(sig_fdr == TRUE ~ "Survives FDR Correction",
                                 sig_uncor == TRUE & sig_fdr == FALSE ~ "Uncorrected Only",
                                 sig_uncor == FALSE & sig_fdr == FALSE ~ "Not Significant")) %>%
  mutate(significant = factor(significant, ordered=TRUE, levels=c("Survives FDR Correction", "Uncorrected Only", "Not Significant")))
```

@@

```{r}
z.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=significant)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

z.sig.sex_diff.violin <- z.feat.sex.test.df %>%
  dplyr::filter(sig_uncor == TRUE) %>%
  ggplot() +
  geom_violin(aes(x=prop, y=median_sex_diff, fill=dataset, color=dataset)) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z-Score Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

@@

z.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_uncor == FALSE ~ NA,
                              TRUE ~ median_sex_diff)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

@@

t.test.z.sex.diff <- z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  # sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                  #                     p.val_fdr >= 0.05 ~ FALSE),
         sig_uncor = case_when(p.val_fdr < 0.05 ~ "*",
                            p.val_fdr >= 0.05 ~ ""),
         y_pos = max_val+0.005)

z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_uncor, y = y_pos),
              data = t.test.z.sex.diff[which(t.test.z.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
```

```{r}
z.t.test.cent.sex.diff <- z.feat.sex.test.df %>%
  dplyr::filter(sig_uncor == TRUE) %>%
  group_by(dataset, prop) %>%
  summarise(w.test.p = tidy(wilcox.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(w.test.p, method="fdr", n = (11)), 
         y_pos = max_val*1.3) %>%
  add_significance("w.test.p", cutpoints = c(0, 0.001, 0.01, 0.05, 1),
  symbols = c("***", "**", "*", "ns"))

z.cent_sex_diff.plt <- z.feat.sex.test.df %>%
  dplyr::filter(sig_uncor == TRUE) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
  geom_jitter(size=0.4, alpha=0.1) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), scales="free_y") + 
  geom_text(aes(label = w.test.p.signif, y = y_pos),
              data = z.t.test.cent.sex.diff) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z-Score Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
z.cent_sex_diff.plt

@@

```{r}
noext_z.feat.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext_z.feat.sex.test.df <- bind_rows(noext_z.feat.sex.test.list) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      sig_uncor = ifelse(p.value<0.05, TRUE, FALSE)) %>%
  mutate(significant = case_when(sig_fdr == TRUE ~ "Survives FDR Correction",
                                 sig_uncor == TRUE & sig_fdr == FALSE ~ "Uncorrected Only",
                                 sig_uncor == FALSE & sig_fdr == FALSE ~ "Not Significant")) %>%
  mutate(significant = factor(significant, ordered=TRUE, levels=c("Survives FDR Correction", "Uncorrected Only", "Not Significant")))
```

@@

```{r}
noext_z.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=significant)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

noext_z.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_uncor == FALSE ~ NA,
                              TRUE ~ median_sex_diff)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")
